New approaches for boosting to uniformity

### 2014-10-04 assets/paperdraft/parts/metrics.tex
deleted multiplication by 10 in SDE

\subsection{Advantages and Disadvantages of Different Metrics}
\subsubsection{Theil and SDE}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some masses distributed uniformly in $[0,1]$, some constant $\alpha$ from interval $[.1,1]$. The predictions are correlated with mass via beta distribution.
We have two distributions that are different in a way that they are symmetrical. SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak. 
First distribution with a peak is obtained by generating a prediction for each event according to it mass:
\[
	p \thicksim \text{Beta}(\alpha \mean{m}, \abs{m - \mean{m}})
\]
while the second one has minus sign in front. Figures~\ref{fig:peakdists}~and~\ref{fig:pitdists} show the distribution of the predictions
and classifier efficiency as a function of mass for the peak and pit distributions, respectively. 
\begin{figure}[h]
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PeakDistributions.png}
			\caption{Mass vs prediction.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PeakEffs.png}
			\caption{Mass vs efficiency. The different coloured lines correspond to
				different global classifier efficiencies, as explained in the legend on the leftmost subplot.}
		\end{subfigure}
		\caption{Peak response distribution and efficiencies as a function of mass. \label{fig:peakdists}}
\end{figure}

\begin{figure}[h]
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PitDistributions.png}
			\caption{Mass vs prediction.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PitEffs.png}
			\caption{Mass vs efficiency. The different coloured lines correspond to
				different global classifier efficiencies, as explained in the legend on the leftmost subplot.}
		\end{subfigure}
		\caption{Pit response distribution and efficiencies as a function of mass. \label{fig:pitdists}}
\end{figure}

@@

From these figures we can see that SDE has the same value and it is not able to make difference between these distributions. In the second case Theil has lower value which indicates that distribution is flatter. In the combination with SDE it can be used to detarmine the type of a distribution. Lower value of SDE can indicate that distribution is flat or has some narrow peaks or pits, and by using Theil we can distinguish between these two cases.

\subsubsection{$D \to hhh$}
When our classifiers where applied to data set $D \to hhh$ we got uniformity measures for the SDE and Theil
metrics shown in Fig.~\ref{fig:d2hhhsdetheil}.
\begin{figure}[h]
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hSignalEffs.png}
			\caption{Metrics for $D \to hhh$ signal.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hBgEffs.png}
			\caption{Metrics for $D \to hhh$ background.}
		\end{subfigure}
		\caption{Uniformity metrics for the $D \to hhh$ data set. The (top) signal and (bottom) background uniformities are plotted as a function of the training stage of a given classifier, listed in the legends on the leftmost plots. \label{fig:d2hhhsdetheil}}
\end{figure}

Both metrics shown similar results, and that there is no significant difference on real data sets (as well as CvM).
The SDE and Theil metrics can be used together in limit cases to more precisely determine nature of a distribution.

>>>>

\subsection{Advantages and Disadvantages of Different Metrics}
\subsubsection{Theil and SDE}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some masses distributed uniformly in $[0,1]$, some constant $\alpha$ from interval $[0,1]$. 
The predictions are correlated with mass via beta distribution.
First distribution with a peak is obtained by generating a prediction for each event according to its mass:
\[
	p_{\rm peak} \thicksim \text{Beta}(\alpha \mean{m}, \abs{m - \mean{m}})
\]
The second distribution is obtained by flipping:
\[
	p_{\rm pit} \thicksim 1 - \text{Beta}(\alpha \mean{m}, \abs{m - \mean{m}})
\]
SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak.

Figures~\ref{fig:peakdists} and~\ref{fig:pitdists} show the distribution of the predictions
and classifier efficiency as a function of mass for the peak and pit distributions, respectively. 
\begin{figure}[h]
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PeakDistributions.png}
			\caption{Mass vs prediction.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PeakEffs.png}
			\caption{Mass vs efficiency. The different coloured lines correspond to
				different global classifier efficiencies, as explained in the legend on the leftmost subplot.}
		\end{subfigure}
		\caption{Peak response distribution and efficiencies as a function of mass. \label{fig:peakdists}}
\end{figure}

\begin{figure}[h]
\centering
		% maybe we can just ignore this?
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PitDistributions.png}
			\caption{Mass vs prediction.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PitEffs.png}
			\caption{Mass vs efficiency. The different coloured lines correspond to
				different global classifier efficiencies, as explained in the legend on the leftmost subplot.}
		\end{subfigure}
		\caption{Pit response distribution and efficiencies as a function of mass. \label{fig:pitdists}}
\end{figure}

@@

From these figures we can see that SDE doesn't make any difference between these distributions, while Theil has lower value in the second case 
which indicates that distribution is flatter. This example demonstrates that Theil has larger penalty for distributions with narrow peaks rather than with narrow pits in the distribution of efficiecies.

\subsubsection{$D \to hhh$}
When our classifiers where applied to data set $D \to hhh$ we got uniformity measures for the SDE and Theil
metrics shown in Fig.~\ref{fig:d2hhhsdetheil}.
\begin{figure}[h]
\centering
		% TODO use metrics on signal for signal, use metrics on bck for bck.
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hSignalEffs.png}
			\caption{Metrics for $D \to hhh$ signal.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hBgEffs.png}
			\caption{Metrics for $D \to hhh$ background.}
		\end{subfigure}
		\caption{Uniformity metrics for the $D \to hhh$ data set. The (top) signal and (bottom) background uniformities are plotted as a function of the training stage of a given classifier, listed in the legends on the leftmost plots. \label{fig:d2hhhsdetheil}}
\end{figure}

Both metrics shown similar results, and that there is no significant difference on real data sets (as well as CvM).
